Income Inequality is revealed in Torontonian Apartment Maintenance

### 2022-02-07 outputs/paper/paper.Rmd
Changed a few words.

## Data discussion

### Societal Impact of Scores

@@

### Bias and Ethical Concerns

@@

### Data Collection Concerns

@@

### Income

@@

As average income was not provided for the data set, we had to collect external data which was set in 2016 and may not be accurate as it is not current to the modern day.
While the N/As were dispersed randomly throughout the data set, removing them may have caused bias in the data set so our analysis of Scores, security and year built may have been different if the N/A values had been filled. Also, removing variables even if they were already present in the Score variable may have caused incorrect analysis as there may be some important information in the rejected variables that either brings a new perspective or aids one of the accepted variable in explaining the relationships between apartment type, ward, maintenance scores and security.

>>>>

# Discussion

## Societal Impact of Scores

@@

## Bias and Ethical Concerns

@@

## Data Collection Concerns

@@

## Income

@@

As average income was not provided for the data set, we had to collect external data which was set in 2016 and may not be accurate as it is not current to the modern day.
While the missing values were dispersed randomly throughout the data set, removing them may have caused bias in the data set so our analysis of Scores, security and year built may have been different if the missing values had been filled. Also, removing variables even if they were already present in the Score variable may have caused incorrect analysis. This is because there may be some important information in the rejected variables that either brings a new perspective or aids one of the accepted variable in explaining the relationships between apartment type, ward, maintenance scores and security.
